Is structure based drug design ready for selectivity optimization?

### 2018-11-01 manuscript.tex
checking in final changes

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure5.png}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-5}
{\bf Relative free energy calculations can accurately predict potency, but show larger errors for selectivity predictions.} \\
}
\end{fullwidth}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%
%%%%%%%%
%%%%%
%%%
%%
%
%
%
%
%    Supplementary Information
%
%

>>>>

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure5.png}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-5}
{\bf Correlation in selectivity prediction errors can be used to accelerate selectivity optimization} \\
{\bf A} (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and ERK2 (Y-axis) from the Bayesian graphical model. (\emph{right}) Speedup in selectivity optimization (Y-axis) as a function of correlation coefficient (X-axis). The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray, while the expected speed up is shown for 100x (green curve) and 10x (yellow curve) selectivity optimization. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. 
{\bf B} (\emph{left}) The same as above, with CDK2 (X-axis) and CDK9 (Y-axis). (\emph{right}) As above, for the CDK2/CDK9 calculations.}
\end{fullwidth}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%
%%%%%%%%
%%%%%
%%%
%%
%
%
%
%
%    Supplementary Information
%
%
\newpage
\section{Supplemental Information}
\setcounter{figure}{0} 
\renewcommand{\figurename}{Supplemental Figure.}

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure1.png}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-1}
{\bf CDK2 adopts an inactive conformation in the crystal structure used for the CDK2/ERK2 calculations} \\
{\bf A} CDK2 (5K4J) adopts an inactive conformation in the absence of its cyclin. The DFG motif is in a DFG-out conformation, with the $\alpha$C helix rotated outwards, breaking the salt bridge between K33 and E51 (Uniprot numbering) that is typically a marker of an active conformation. 
{\bf B} The CDK2 strucutre used for the CDK2/CDK9 calculations (4BCK) contains cyclin A, and surprisingly, adopts a DFG-out conformation forms the salt bridge between K33 and E51. 
}
\end{fullwidth}
\end{figure}
